### 2014-11-13 tex/intro.tex
Focused language

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. Our
inspiration is found in the domain of static analysis that uses sets
of constraints over heap locations to encode multiple heaps in a
single representation. These sets, sometimes known as value sets or
value summaries, allow multiple heaps to be represented simultaneously
with a higher degree of precision than afforded by traditional
techniques for shape analysis.

Unfortunately, value sets often do not support aliasing and require a
recursive definition of objects~\cite{..}. Also, it is not obvious how
to support heap updates in value sets, and in particular, on-the-fly
lazy initialization as is common in GSE, so it is not unusual to
require a fully initialized set of input heaps in the analysis. As is
typical in static analysis, over approximation of the value sets
alleviates some of the limitations but also leads to false positives,
and when heap updates are supported, with or without over
approximation, the path constraint must be rewritten to reflect the
update, and the constraints in the value set must also be rewritten.

@@

The solution presented in this paper to enabling value sets in symbolic execution
with lazy initialization is to represent the heap as a bipartite graph
consisting of references and locations. A reference is able to point
to several different locations; each edge is predicated on constraints
over aliasing between references. Locations point back to references
on different fields. The bipartite graph enables (i) the use of
aliasing to define objects rather than recursive definitions; (ii)
value set computation using only local information; and (iii) heap
updates that only impact affected locations, require no constraint
rewriting, and require no auxiliary variables in the constraints.  We
call this new heap a summary heap.

@@

Aside from the novelty of the heap summary and it application to
symbolic execution, the new data structure appears to ameliorate state
explosion in symbolic execution. A preliminary implementation in Java
Pathfinder (JPF), described in this paper, compares the heap summary
algorithm on a handful of benchmarks, each representing different
degrees of initialization and branching, to GSE with lazy
initialization in Symbolic Pathfinder (SPF) and implementation
lazier\# also in SPF. The results show that in general, that the heap
summary algorithm improves over other techniques, and in some
instances, the improvement is remarkable: two-orders of magnitude
reduction in running time. More critically though, the heap summary
enables the initialization of larger more complex heaps than
heretofore possible as shown in our results.

@@

\begin{description}

@@

\end{description}

\noindent{The rest of this paper discusses a formal language semantics
  for the summary heap algorithm definition with the definition of the
  summary heap. The paper then presents the application of summary
  heaps to symbolic execution. Following the algorithm definition, the
  existence proof of bisimulation is given with the accompanying
  corollaries for soundness and completeness. This is followed by the
  implementation in JPF and the evaluation. The paper ends with the
  conclusion and future work.}

>>>>

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. Our
inspiration is found in the domain of static analysis that uses sets
of constraints over heap locations to encode multiple heaps in a
single representation. These sets, sometimes known as \emph{value sets} or
\emph{value summaries}, allow multiple heaps to be represented simultaneously
with a higher degree of precision than afforded by traditional
techniques for shape analysis.

Unfortunately, value sets often do not support aliasing and require a
recursive definition of objects~\cite{..}. Also, heap updates often
require that the path constraint be rewritten to reflect the update,
and the constraints in the value set may also need to be rewritten with the
addition of auxiliary variables. These non-local operations make it
difficult to use value sets in symbolic execution. As is
typical in static analysis, over approximation of the value sets
alleviates some of the limitations but also leads to false positives.

@@

The solution presented in this paper to enabling value sets in symbolic execution
with lazy initialization is to represent the heap as a bipartite graph
consisting of references and locations. A reference is able to point
to several different locations: each edge predicated on constraints
over aliasing between references. Locations point back to references
on different fields. The bipartite graph enables (i) the use of
aliasing to define objects rather than recursive definitions; (ii)
value set computation using only local information; and (iii) heap
updates that only impact affected locations, require no constraint
rewriting, and require no auxiliary variables in the constraints.  We
call this new heap a summary heap.

@@

Aside from the novelty of the heap summary and its application to
symbolic execution, the new data structure appears to ameliorate state
explosion in symbolic execution as hoped. A preliminary implementation in Java
Pathfinder (JPF), described in this paper, compares the heap summary
algorithm on a handful of benchmarks, each representing different
degrees of initialization and branching, to GSE with lazy
initialization in Symbolic Pathfinder (SPF) and implementation
lazier\# also in SPF. The results show that in general, that the heap
summary algorithm improves over other techniques, and in some
instances, the improvement is remarkable: two-orders of magnitude
reduction in running time. More critically though, the heap summary
enables the initialization of larger more complex heaps than
heretofore possible as shown in our results.

@@

\begin{compactdesc}

@@

\end{compactdesc}
The rest of this paper defines summary heap and its to symbolic
execution. Following the algorithm definition, the existence proof of
bisimulation is given with the accompanying corollaries for soundness
and completeness. This is followed by the implementation in JPF and
the evaluation. The paper ends with the conclusion and future work.
